---
output:
  md_document:
    variant: markdown_github
---
Financial Econometrics Practical
# Outline

This Readme will outline all the following questions by means of explaining, interpreting and reasoning through all the necessary code and functions, whereafter a simplified output will be reproduced within each respective question folders.

First, I sanitize our working environment and source all the necessary functions that will be incorporated into our analyses.
```{r, include=FALSE}

rm(list = ls())
gc()
library(tidyverse)
list.files('code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))
```

```{r}
# this is a commented out chunk indicating the process by which the questions folders where produced.

# HTML Texevier:
#Texevier::create_template_html(directory = "/Users/michaelbrand/OneDrive/Documents/UNI/2021/2/Fin.Metrics/Test/21270945/Questions",
 #                         template_name = "Question1"
#)
#Texevier::create_template_html(directory = "/Users/michaelbrand/OneDrive/Documents/UNI/2021/2/Fin.Metrics/Test/21270945/Questions",
#                         template_name = "Question2"
#)
#Texevier::create_template_html(directory = "/Users/michaelbrand/OneDrive/Documents/UNI/2021/2/Fin.Metrics/Test/21270945/Questions",
#                         template_name = "Question3"
#)
#Texevier::create_template_html(directory = "/Users/michaelbrand/OneDrive/Documents/UNI/2021/2/Fin.Metrics/Test/21270945/Questions",
#                          template_name = "Question4"
#)
#Texevier::create_template_html(directory = "/Users/michaelbrand/OneDrive/Documents/UNI/2021/2/Fin.Metrics/Test/21270945/Questions",
#                          template_name = "Question5"
#)
#Texevier::create_template_html(directory = "/Users/michaelbrand/OneDrive/Documents/UNI/2021/2/Fin.Metrics/Test/21270945/Questions",
#                          template_name = "Question6"
#)
```
Now I procceed with the respective questions.

# Question 1: Yield Spread

